Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2020-09-19 papers/paper/paper.tex
Added plots to front page of paper

>>>>

\section*{Plots from MC}
\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/final_disp_probability_distribution_5.50e+09_1.00e+09.pdf}
\caption{\textbf{Probability distribution plot of final displacement vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:final_disp_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_probability_distribution_5.50e+09_1.00e+09.pdf}
\caption{\textbf{Probability distribution plot of step length vs. initial displacement.} Dimentions: $nm^{-2}$ (Probability per area of box).}
\label{fig:step_length_prob}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/step_length_1d_probability_density_5.50e+09_1.00e+09.pdf}
\caption{\textbf{Probability density of step lengths.} Dimentions: $nm^{-1}$ (Probability per nm).}
\label{fig:step_length_prob_den}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/prob_lagging_vs_init_L_5.50e+09_1.00e+09.pdf}
\caption{\textbf{Probability of lagging step vs. initial L.} Dimentions: dimensionless (Probability).}
\label{fig:prob_lagging}
\end{figure}

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/mc_plots/bb_time_5.50e+09_1.00e+09.pdf}
\caption{\textbf{Bothbound Time.} Dimentions: $s$ .}
\label{fig:bothbound_time}
\end{figure}

\newpage
